More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-11 2016-Weak-FH-Bisim/WeakBisim.tex
modifs
update tres leger pages 12-15

 Then 
$\mathcal{R}$ is an FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
have
the following:
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
\end{minipage}

@@

This section defines the semantics of an open \pNet as a translation into an open automaton. 
In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition. The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the 
This allows us to derive a bismulation theory for open \pNet s. As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.

@@

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
a subnet. One of its possible open transition (synchronizing the hole $P$
with the \emph{Protocol}) is:

@@

\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.

\begin{figure}[bh]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\OTarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \OTarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
  ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
  \label{usingrules:OT2}
\end{figure}

@@

\subsection{Computing and using open automata}
\TODO{REMOVE?}
In this section we present a simple algorithm to construct the open
automaton representing the behaviour of an open pNet, and we prove that
under reasonable conditions this automaton is finite.

% \TODO{Eric: refine the algorithm description - \ERIC{Done, can you check ?}}

@@

\subsection{Bisimulation for open \pNet s and Composability}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open \pNet s:
\begin{definition}[FH-bisimulation for open \pNet s]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
\end{definition}
We can now prove that \pNet\ composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a \pNet\ is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation.

>>>>

 Then 
$\mathcal{R}$ is an FH-bisimulation iff for any  states
$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
have
the following:
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
\end{minipage}

@@

This section defines the semantics of an open \pNet as a translation into an open automaton. 
In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition. The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
\TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
This allows us to derive a bismulation theory for open \pNet s. As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.

@@

%%\TODO{rewrite example with new OTs}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
At the upper level, the $ABP$ pNet has 2 holes and $Protocol$ has
a subnet. One of its possible open transitions (synchronizing the hole $P$
with the \emph{Protocol}) is:

@@

\TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.

\begin{figure}[h]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\OTarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \OTarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
  ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
  \label{usingrules:OT2}
\end{figure}

@@

\subsection{Computing and using open automata}
\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
In this section we present a simple algorithm to construct the open
automaton representing the behaviour of an open pNet, and we prove that
under reasonable conditions this automaton is finite.

@@

\subsection{Bisimulation for open pNets and Composability}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open \pNet s:
\begin{definition}[FH-bisimulation for open \pNet s]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
\end{definition}
We can now prove that \pNet\ composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a \pNet\ is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation.
